---
title: "DualPAMImportData"
author:
- Julie A. Nadeau
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE   
csl: plos-one.csl
---

This .Rmd imports and tidys underlying data from the DualPAM kinetic fluorometer/absorbtometer software, along with culture MetaData and Turner Chlorophyll data. 

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```


```{r conversions}
us_s <- 1000000
photons_umol <- 6.022E17
A2_m2 <- 1E20
```

```{r load libraries}
library(tidyverse)
library(lubridate)
library(photobiologyWavebands) #R colours from nm values
library(broom) #formatting model outputs

#https://googlesheets4.tidyverse.org/
library(googledrive)
library(googlesheets4)

```


# Set Project Variables

```{r set project variables}
Project <- "PICO"
DataOut <- file.path("..", "Data", "ProcessedData")


NoO2Runs <- c("JuNa1201", "JuNa1202", "JuNa1203", "JuNa1204", "JuNa1205")
BadRuns <- c("JuNa1215")
DubiousRuns <- c("JuNa1206", "JuNa1207", "JuNa1208", "JuNa1209", "JuNa1210")

DualPAMMeta <- readRDS(file = file.path("..", "Data", "ProcessedData", "PICO_O2Analyses_DualPAMMeta.Rds"))

colnames(DualPAMMeta)

DualPAMMEta <- DualPAMMeta |>
  select(-c(`...46`, `...47`)) |>
  select(-c("ID.y", "MediaDate","Source","SourceSalinity","Optode","OptodeCh","InocpH","FinalpH","ExpEndDate" )) |>
  rename(ID = ID.x)

```


```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c(w_length2rgb(Wavelengths_nm[1]), w_length2rgb(Wavelengths_nm[2]), w_length2rgb(Wavelengths_nm[3]), w_length2rgb(Wavelengths_nm[4]), w_length2rgb(Wavelengths_nm[5]))

names(Colours_nm) <- Wavelengths_nm
Colours_nm

```






```{r DualPAMData plot}


DualPAMMeta |>
  ggplot() +
  geom_point(aes(x = PAR, y = YI), colour = "blue") +
  geom_point(aes(x = PAR, y = YII), colour = "red") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, SampleID)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  filter(Strain == "PCC9511") |>
  ggplot() +
  geom_point(aes(x = PAR, y = YI), colour = "blue") +
  #geom_point(aes(x = PAR, y = YII), colour = "red") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "Strain, Growthlight_uE, O2_Category", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "MeasureO2_uM", breaks = NULL, labels = NULL)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  filter(Strain == "MIT9313") |>
  ggplot() +
  geom_point(aes(x = PAR, y = YI), colour = "blue") +
  geom_point(aes(x = PAR, y = YII), colour = "red") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
    filter(Strain == "PCC9511") |>
    filter(OptodeMeasure == 1) |>
  ggplot() +
  geom_point(aes(x = YI, y = YII, colour = as.factor(OptodeMeasure))) +
  #geom_smooth(aes(x = YI, y = YII), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
    filter(Strain == "MIT9313") |>
    filter(OptodeMeasure == 1) |>
  ggplot() +
  geom_point(aes(x = YI, y = YII, colour = as.factor(OptodeMeasure))) +
  #geom_smooth(aes(x = YI, y = YII), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

```
PAR <- umol photons m^-2 s^-1 applied during the measurement
YI <- photochemical yield of PSI
Self Starting Exponential Decay Function
https://douglas-watson.github.io/post/2018-09_exponential_curve_fitting/

Possible issue with std.error_log_alpha converted back through exp(td.error_log_alpha)
```{r fit self starting exponential decay}
YFits <-   DualPAMMeta |>
  filter(PAR < 600) |>  #possible issue with row labelling of PAR in data files?
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  nest(data = -c(Strain, O2_Category, MeasureO2_uM, Par_ue)) %>%
  mutate(
    YIfit = map(data, possibly(~nls(YI ~ SSasymp(PAR, YIf, YI0, log_alpha), data = .), NULL)),
    YItidied = map(YIfit, tidy),
    YIaugmented = map(YIfit, augment)
  ) |>
  mutate(
    YIIfit = map(data, possibly(~nls(YII ~ SSasymp(PAR, YIIf, YII0, log_alpha), data = .), NULL)),
    YIItidied = map(YIIfit, tidy),
    YIIaugmented = map(YIIfit, augment)
    ) |>
  mutate(
    qPfit = map(data, possibly(~nls(qP ~ SSasymp(PAR, qPf, qP0, log_alpha), data = .), NULL)),
    qPtidied = map(qPfit, tidy),
    qPaugmented = map(qPfit, augment)
  )  

YFits

#Filter for any row where fit failed for any combination; temporary hack, MIT9313 Intermediate O2, Par_ue 90, YI fit failed
#smarter way to do this by selecting multiple columns
YFitsFilter <- YFits |>
  drop_na(YIfit, YIIfit, qPfit)
  #be careful if both NULL and NA present       
 

YIFitValues <- YFits |>
  unnest(YItidied) |>
  select(Strain, O2_Category, MeasureO2_uM, Par_ue, term, estimate, std.error) |> 
  pivot_wider(names_from = c(term), values_from = c(estimate, std.error)) |>
  mutate(alpha = exp(estimate_log_alpha),
         alpha_se = exp(std.error_log_alpha),
         YIPARHalf = log(2)/alpha) |>
  select(-c(estimate_log_alpha, std.error_log_alpha))

YIIFitValues <- YFits |>
  unnest(YIItidied) |>
  select(Strain, O2_Category, MeasureO2_uM, Par_ue, term, estimate, std.error) |> 
  pivot_wider(names_from = c(term), values_from = c(estimate, std.error)) |>
  mutate(alpha = exp(estimate_log_alpha),
         alpha_se = exp(std.error_log_alpha), 
         YIIPARHalf = log(2)/alpha) |>
  select(-c(estimate_log_alpha, std.error_log_alpha))

qPFitValues <- YFits |>
  unnest(qPtidied) |>
  select(Strain, O2_Category, MeasureO2_uM, Par_ue, term, estimate, std.error) |> 
  pivot_wider(names_from = c(term), values_from = c(estimate, std.error)) |>
  mutate(alpha = exp(estimate_log_alpha),
         alpha_se = exp(std.error_log_alpha), 
         qPPARHalf = log(2)/alpha) |>
  select(-c(estimate_log_alpha, std.error_log_alpha))


Y_PAR_FitValues <- left_join(YIFitValues, YIIFitValues, by = join_by(Strain, O2_Category, MeasureO2_uM, Par_ue), suffix = c("YI", "YII")) |>
  left_join(qPFitValues, by = join_by(Strain, O2_Category, MeasureO2_uM, Par_ue), suffix = c("Y", "qP"))

head(Y_PAR_FitValues)

#rm(YIFitValues, YIIFitValues, qPFitValues)

```

```{r exponential decay fit plots}
#YFits Filtered for any failure

YFits |>
  unnest(YIaugmented) |>
  ggplot() + 
  geom_line(aes(x = PAR, y = .fitted), colour = "blue") +
  geom_point(aes(x = PAR, y = YI)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  labs(title = "YI") +
  theme_bw()
  
  YFits |>
  unnest(YIIaugmented) |>
  ggplot() + 
  geom_line(aes(x = PAR, y = .fitted), colour = "red") +
  geom_point(aes(x = PAR, y = YII)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  labs(title = "YII") +
  theme_bw()
  
  YFits |>
  unnest(qPaugmented) |>
  ggplot() + 
  geom_line(aes(x = PAR, y = .fitted), colour = "black") +
  geom_point(aes(x = PAR, y = qP)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  labs(title = "qP") +
  theme_bw()
 
  #left_join creating new rows b/c YIIaugmented and qPaugmented have more successful fits than YI augmented so multiple row matching.
  #filter out fits where any fit YI, YII, qP failed
  #still issue with many to many relation; duplicating rows???
  #partially issue with PAR values; different for different parameters YI, YII, qP?
  
# Y_PAR_PredictValues <- left_join(x = YFitsFilter |> unnest(YIaugmented) |> filter(PAR != 0), y = YFitsFilter |> unnest(YIIaugmented) |> filter(PAR != 0), by = join_by(Strain, O2_Category,Par_ue,  MeasureO2_uM, PAR), suffix = c(".YI", "YII")) |>
#  select(c("Strain", "O2_Category", "Par_ue", "MeasureO2_uM", "PAR", "YI",".fitted.YI",".resid.YI","YII",".fittedYII",      ".residYII"))
# 
# Y_PAR_PredictValues2 <- left_join(x = Y_PAR_PredictValues, y = YFitsFilter |> unnest(qPaugmented) |> filter(PAR != O), by = join_by("Strain", "O2_Category", "Par_ue", "MeasureO2_uM", "PAR"))
# 
# |>
#   select(c("MeasureO2_uM","Strain","Par_ue","O2_Category","YI","PAR",".fitted.YI",".resid.YI","YII",".fittedY2",      ".residY2"))
# 
# 
# |>
#   cbind(y = YFits |> unnest(qPaugmented) |> select("qP",".fitted",".resid"))




#        "YIfitY2"        "YItidiedY2"     "YIaugmented.x" 
#[22] "YIIfitY2"       "YIItidiedY2"    "YII"            ".fittedY2"      ".residY2"       "qPfitY2"        "qPtidiedY2"    
#[29] "qPaugmentedY2"  "data"           "YIfit"          "YItidied"       "YIaugmented.y"  "YIIfit"         "YIItidied"     
#[36] "YIIaugmented.y" "qPfit"          "qPtidied"       "qP"             ".fitted"        ".resid" )) |>
 
  # [1] "MeasureO2_uM"   "Strain"         "Par_ue"         "O2_Category"    "data.YI"        "YIfit.YI"       "YItidied.YI"   
 #[8] "YI"             "PAR"            ".fitted.YI"     ".resid.YI"      "YIIfit.YI"      "YIItidied.YI"   "YIIaugmented.x"
#[15] "qPfit.YI"       "qPtidied.YI"    "qPaugmented.YI" "dataY2"         "YIfitY2"        "YItidiedY2"     "YIaugmented.x" 
#[22] "YIIfitY2"       "YIItidiedY2"    "YII"            ".fittedY2"      ".residY2"       "qPfitY2"        "qPtidiedY2"    
#[29] "qPaugmentedY2"  "data"           "YIfit"          "YItidied"       "YIaugmented.y"  "YIIfit"         "YIItidied"     
#[36] "YIIaugmented.y" "qPfit"          "qPtidied"       "qP"             ".fitted"        ".resid" 
   
  
# Y_PAR_PredictValues |>
#   ggplot() + 
#   geom_point(aes(x = YI, y = YII)) +
#   geom_line(aes(x = `.fitted.x`, y = `.fitted.y`), colour = "green") +
#   facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
#   #labs(x = "YI", y = "YII") +
#   theme_bw()

```
```{r exponential decay parameter plots}
Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = alphaYI, y = alphaYII, colour = as.factor(MeasureO2_uM))) +
  facet_grid(cols = vars(Strain), rows = vars(Par_ue, O2_Category)) +
  theme_bw()

Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = YIPARHalf, y = YIIPARHalf, colour = as.factor(MeasureO2_uM))) +
  facet_grid(cols = vars(Strain), rows = vars(Par_ue, O2_Category)) +
  theme_bw()


Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = MeasureO2_uM, y = alphaYI, colour = as.factor(Par_ue))) +
  facet_grid(cols = vars(Strain), rows = vars(Par_ue, O2_Category)) +
  theme_bw()

Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = MeasureO2_uM, y = alphaYII, colour = as.factor(Par_ue))) +
  facet_grid(cols = vars(Strain), rows = vars(Par_ue, O2_Category)) +
  theme_bw()

Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = MeasureO2_uM, y = YIPARHalf, colour = as.factor(Par_ue))) +
  facet_grid(cols = vars(Strain), rows = vars(O2_Category)) +
  theme_bw()

Y_PAR_FitValues |>
  ggplot() +
  geom_point(aes(x = MeasureO2_uM, y = YIIPARHalf, colour = as.factor(Par_ue))) +
  facet_grid(cols = vars(Strain), rows = vars(O2_Category)) +
  theme_bw()

```

```{r ynd yna plots}
DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  ggplot() +
  geom_point(aes(x = PAR, y = YND), colour = "red") +
  geom_point(aes(x = PAR, y = YNA), colour = "black") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  ggplot() +
  geom_point(aes(x = YND, y = YNA)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = YND, y = YNA)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = YI, y = YND)) +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = YII, y = (1-YND))) +
  geom_smooth(aes(x = YII, y = (1-YND)), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = YII, y = (1-YNA))) +
  geom_smooth(aes(x = YII, y = (1-YNA)), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = qP, y = (1-YNA))) +
  geom_smooth(aes(x = qP, y = (1-YNA)), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()
  
DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = qP, y = (1-YND))) +
  geom_smooth(aes(x = qP, y = (1-YND)), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()

DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = qP, y = (YI))) +
  geom_smooth(aes(x = qP, y = (YI)), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()
```

``` {r DualPamLRC, fig.cap = "Light response curves of PSI electron transport (e- PSI-1 s-1) for two *Prochlorococcus* strains after growth under different combinations of light level and oxygen concentration. The blue and red points represent the experimental data.", out.height="800pt", out.width="100%", echo = FALSE}}
DualPAMMeta |>
  filter(MeasureO2_uM %in% c(2, 25, 250)) |>
  #filter(!(SampleID %in% NoO2Runs)) |>
  filter(!SampleID %in% BadRuns) |>
  filter(OptodeMeasure == 1) |>
  #filter(O2_Category != "Low") |>
  filter(Par_ue == 30) |>
  ggplot() +
  geom_point(aes(x = PAR, y = YI), colour = "blue") +
  geom_point(aes(x = PAR, y = qP), colour = "red") +
  #geom_smooth(aes(x = PAR, y = qP), method = "lm") +
  facet_grid(cols = vars(MeasureO2_uM), rows = vars(Strain, Par_ue, O2_Category)) +
  theme_bw()
  
```


```{r save DualPAMMeta}
 saveRDS(Y_PAR_FitValues, file.path(DataOut, paste(Project, "Y_PAR_FitValues.Rds", sep = "_"), fsep = .Platform$file.sep))

```
