---
title: "SolisenseImportData"
author:
- Maximilian Berthold
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE   
csl: plos-one.csl
---

This .Rmd imports and tidys underlying data from the Solisense kinetic fluorometer software.
It does not perform the underlying fits of the induction/relaxation profiles from FRRf protocols.

  
# Set Chunk Options


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Set Project Variables
```{r set project variables}
Project <- "PICO"
DataOut <- file.path("..", "Data", "ProcessedData")
CalibData <- file.path("..", "Data",  "CalibrationData")

Run <- "O2Analyses"

ExpDate <- "2023-05-27" #date of first MultiCulti growth start

DataIn <- file.path("..", "Data", "RawData", "Solisense", fsep = .Platform$file.sep)

FileID <- "data"

Catalog <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

ChlTurner <- "https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0"

FileEncode <- "UTF-8" 
Delimiter <- ","

HeaderRows <- 14

```

```{r conversions}
us_s <- 1000000
photons_umol <- 6.022E17
A2_m2 <- 1E20
```


```{r load libraries}
library(tidyverse)
library(lubridate)
library(photobiologyWavebands) #R colours from nm values
library(broom) #formatting model outputs

#https://googlesheets4.tidyverse.org/
library(googledrive)
library(googlesheets4)

```

Load Multiculti catalog and ChlTurner
```{r load multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
# MultiCulti metadata
MetaData <- read_sheet(Catalog)%>%
  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaData)

MetaData <- MetaData %>%
   mutate(ExpDate = lubridate::ymd(ExpDate),
          ExpEndDate = lubridate::ymd_hms(`ExpEndDate`))
# find units for chl
ChlData <- read_sheet(ChlTurner) |>
  mutate(Chl = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept))

```

```{r read ActPAR calibration files}
#ActPARCal <- readRDS("~/Dropbox/CampbellLabProtocols/ChlorophyllFluorescence/SolisenseInformation/SolisenseInformation_DCCalibParam.Rds")

ActPARCrossCal <- list.files(path = CalibData, full.names = TRUE)  %>%
       map_df(~readRDS(file  = .))

#intercept set to 0 in lm in SolisenseInformation.Rproj/SolisenseCalibCompare.Rmd
ActPARCrossCal <- ActPARCrossCal |>
  rename(#Intercept = `estimate_(Intercept)`,
         Slope = `estimate_LIFT_Gen_Developer.cal`,
         #Intercept_SE = `std.error_(Intercept)`,
         Slope_SE = `std.error_LIFT_Gen_Developer.cal`)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c(w_length2rgb(Wavelengths_nm[1]), w_length2rgb(Wavelengths_nm[2]), w_length2rgb(Wavelengths_nm[3]), w_length2rgb(Wavelengths_nm[4]), w_length2rgb(Wavelengths_nm[5]))

names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

```{r list Solisense Data files for file import}
SolisenseDataFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE, recursive = FALSE)

SolisenseDataFiles

#test for duplicate file names
unique(duplicated(SolisenseDataFiles))
```


```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}

#a read function using tidyverse::read_delim that skips a fixed number of header rows, and adds columns to the dataframe containing the filename and the file creation date time.
read_delim_plus <- function(flnm, delimiter, headerrows, fileencode){read_delim(flnm, delim = delimiter,  col_names = TRUE,  skip = headerrows, escape_double = FALSE,  locale = locale(encoding = fileencode), trim_ws = TRUE) %>%
    mutate(Filename = flnm)
}

read_delim_SolLight <- function(flnm, delimiter, headerrows, fileencode){DataFile <- read_delim(flnm, delim = delimiter,  col_names = TRUE,  skip = headerrows, escape_double = FALSE,  locale = locale(encoding = fileencode), trim_ws = TRUE) |>
    mutate(Filename = flnm) |> filter(!`DataPt` %in% HeaderRowValues) |>
  filter(`Time(us)` != "99") |>
  select(-c(`...6`)) |>
  rename(Time_us = `Time(us)` )
  
  Lights <- read_delim_plus(flnm, delimiter = Delimiter, headerrows = 0, fileencode = FileEncode) |>
  filter(`----` == "Light:") |>
  separate(`...2`, c("L1","L2","L3","L4","L5"), sep = ",", remove = TRUE) |>
  select(-c("----"))
  
  LightsLength <- tidyr::uncount(tibble(Lights), nrow(DataFile)/nrow(Lights)) |>
  select(-c(Filename))
  
  SolFile <- cbind(DataFile, LightsLength) |>
  filter(DataPt != "==========") |>
  type_convert()
}
  

```

Read Test File
```{r read example Solisense Data file}
# #issue with rows with --------;  easy to filter though
# DataHeaderRows <- 14
# 
# HeaderRowValues <- c("DateTime:", "RFID_EPC:", "RFID_UserData:", "Barcode:", "PIF:", "PARs:", "Light:", "Cycles:", "Lamps:", "Gain:", "SNR_raw:", "Position:", "DataPt", "----")
# 
# 
# TestFile <- read_delim_plus(flnm = "../Data/RawData/Solisense/PICO_202305310950_JuNa1188_445_25_data.csv", delimiter = Delimiter, headerrows = DataHeaderRows, fileencode = FileEncode) |>
#   filter(!`DataPt` %in% HeaderRowValues) |>
#   filter(`Time(us)` != "99") |>
#   select(-c(`...6`)) |>
#   rename(Time_us = `Time(us)` )
# 
# TestLights <- read_delim_plus(flnm = "../Data/RawData/Solisense/PICO_202305310950_JuNa1188_445_25_data.csv", delimiter = Delimiter, headerrows = 0, fileencode = FileEncode) |>
#   filter(`----` == "Light:") |>
#   separate(`...2`, c("L1","L2","L3","L4","L5"), sep = ",", remove = TRUE) |>
#   select(-c("----"))
# 
# #Now expand TestLights to appropriate number of rows for each light...
# 
# CurveLength <- nrow(TestFile)/nrow(TestLights)
# 
# #https://stackoverflow.com/questions/62935872/i-want-to-duplicate-observations-rows-in-a-tibble
# 
# TestLightsLength <- tidyr::uncount(tibble(TestLights), nrow(TestFile)/nrow(TestLights)) |>
#   select(-c(Filename))
# 
# TestFile <- cbind(TestFile, TestLightsLength) |>
#   filter(DataPt != "==========") |>
#   type_convert()
#   
# 
# head(TestFile)

```

```{r testplot}
TestFile |>
  ggplot() +
  geom_point(aes(x = DataPt, y = EM), colour = "red") +
  #geom_point(aes(x = DataPt, y = Fit), size = 0.1) +
  facet_grid(cols = vars(L1)) +
  theme_bw()
  
```
```{r read example Solisense Data file onestep}
DataHeaderRows <- 14

HeaderRowValues <- c("DateTime:", "RFID_EPC:", "RFID_UserData:", "Barcode:", "PIF:", "PARs:", "Light:", "Cycles:", "Lamps:", "Gain:", "SNR_raw:", "Position:", "DataPt", "----")


TestFileOneStep <- read_delim_SolLight(flnm = "../Data/RawData/Solisense/PICO_202305310950_JuNa1188_445_25_data.csv", delimiter = Delimiter, headerrows = DataHeaderRows, fileencode = FileEncode)

```


purrr::map to read all files, two step
```{r read Solisense files}
# SolData <- SolisenseDataFiles |>
#   map_df(~read_delim_plus(flnm =., delimiter = Delimiter, headerrows = DataHeaderRows, fileencode = FileEncode)) |>
#    filter(!`DataPt` %in% HeaderRows) |>
#   filter(`Time(us)` != "99") |>
#   select(-c(`...6`)) |>
#   rename(Time_us = `Time(us)` )
# 
# head(SolData)
# colnames(SolData)
# length(unique(SolData$Filename))
# 
# SolLights <- SolisenseDataFiles |> 
#   map_df(~read_delim_plus(flnm = ., delimiter = Delimiter, headerrows = 0, fileencode = FileEncode)) |>
#   filter(`----` == "Light:") |>
#   separate(`...2`, c("L1","L2","L3","L4","L5"), sep = ",", remove = TRUE) |>
#   select(-c("----"))
# 
# SolLightsLength <- tidyr::uncount(tibble(SolLights), nrow(SolData)/nrow(SolLights)) |>
#   select(-c(Filename))
# 
# SolData <- cbind(SolData, SolLightsLength) |>
#   filter(DataPt != "==========") |>
#   type_convert()
#   
# 
# head(SolData)


```
purrr::map to read all files, onestep read_delim_SolLight function
```{r read Solisense files}
SolData2 <- SolisenseDataFiles |>
  map_df(~ read_delim_SolLight(flnm =., delimiter = Delimiter, headerrows = DataHeaderRows, fileencode = FileEncode))


head(SolData)
colnames(SolData2)
length(unique(SolData2$Filename))


```

```{r SolData plot}
SolData |>
   ggplot() +
  geom_point(aes(x = DataPt, y = EM), colour = "red") +
  #geom_point(aes(x = DataPt, y = Fit), size = 0.1) +
  facet_grid(cols = vars(L1), rows = vars(Filename)) +
  theme_bw()
  
```


XXXXUpdated to here for data import, 12 July 2023XXXX


```{r actparcorr}
#Add ActPARcorr with proper correction factors for TC and no TC
#Intercepts for cross conversions set to 0.

#Some smarter way to do this with map etc....
SolFitsTrim <- SolFitsTrim |> 
  mutate(nm445Corr = case_when(TempCont == "TC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
         nm470Corr = case_when(TempCont == "TC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
         nm505Corr = case_when(TempCont == "TC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
           nm535Corr = case_when(TempCont == "TC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
          nm590Corr = case_when(TempCont == "TC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
          IRCorr = case_when(TempCont == "TC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]))

head(SolFitsTrim)


SolFitsTrim <- SolFitsTrim %>%
  mutate(ActPAR = nm445 + nm470 + nm505 + nm535 + nm590 + IR) |>
  mutate(ActPARCorr = nm445Corr + nm470Corr + nm505Corr + nm535Corr + nm590Corr + IRCorr)#better ways to do this?

head(SolFitsTrim)

```

```{r durations}
#generate column with duration of light step in s
#add a column adding Dark1s based upon any step < 5 s
#replace NA for first dark with nominal 181;  issue will be changing durations of light steps across each run
SolFitsTrim <- SolFitsTrim %>%
  group_by(SourceDataFile, Filename, Project, CultureID, ObsDate, Ex_WL, TempCont) %>%
  #mutate(Step_s = as.numeric(ObsDateTime - lag(ObsDateTime)), .after = ObsDateTime) %>%
  mutate(Step_s = replace_na(as.numeric(ObsDateTime - lag(ObsDateTime)), 181), .after = ObsDateTime) %>% 
  mutate(LR_s = as.numeric(ObsDateTime - ObsDateTime[1]), .after = Step_s) %>%
  mutate(Dark1s = if_else(Step_s > 5, 0, 1), .after = Step_s) %>%
  relocate(Ex_WL, .after = Dark1s) %>%
  relocate(ActPAR, .after = Ex_WL) %>%
  ungroup()
#Figure out how to cope with final step at 0 PAR, not followed by Dark1s step
#separate Dark1s rows
#Figure out how to re-match Dark1s to appropriate light steps

```

```{r}
# test <- SolFitsTrim %>%
#   filter(Ex_WL == "505" & CultureID == "SySl1191")
```


```{r prelimplots}
SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = FvFm, colour = MeasureO2_uM)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = FvFm, colour = MeasureO2_uM, size = ActPARCorr)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL, MeasureO2_uM), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  filter(Tau2QA < 20000) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = Tau2QA, colour = MeasureO2_uM, size = LR_s)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  #filter(Dark1s != 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = Alp2QA, colour = MeasureO2_uM, size = LR_s)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw() 

```




Oxborough & Baker 1997 for Fo'
```{r estimate parameters}
#think about nest_by and map?
SolFitsTrim2 <- SolFitsTrim %>%
  mutate(WtTau = ((Alp1QA * Tau1QA) + (Alp2QA * Tau2QA) + (Alp3QA * Tau3QA)),
         InvWtTau = 1/WtTau,
         Sig_m2psii = Sig/1E20,
         ActPAR_photonsm2s = ActPAR *  6.022e17,
         C_WtTau = 1/(1 + (Sig_m2psii * ActPAR_photonsm2s * (WtTau /us_s)))
         ) %>%
  nest(.by = c(CultureID, Ex_WL, SourceDataFile, Filename, ObsDate )) %>%
   mutate(Fodark = map(data, ~.$Fo[1]),
          Fmdark = map(data, ~.$Fm[1]),
          Fomin = map(data, ~min(.$Fo, na.rm = TRUE)), 
          Fmmax = map(data, ~max(.$Fm, na.rm = TRUE)),
          Sigdark = map(data, ~.$Sig[1]),
          Sigmax = map(data, ~max(.$Sig, na.rm = TRUE)),
          qp = map(data, ~(.$Fm - .$Fo)/(.$Fm - lead(.$Fo)))
          ) %>%
  unnest(cols = c(data, Fodark,Fmdark,Fomin, Fmmax,Sigdark,Sigmax, qp)) %>%
  mutate(aLHIIdark = (Fmdark * Fodark)/(Fmdark - Fodark),
         aLHIIminmax = (Fmmax * Fomin)/(Fmmax - Fomin),
         FoOxbo = Fomin/(((Fmmax - Fomin)/Fmmax) + (Fomin/Fm)),
         qpOxbo = (Fm - Fo)/(Fm - FoOxbo),
         JVPSII_aLHIIminmax = ActPAR_photonsm2s * aLHIIminmax * FvFm,
         JVPSII_aLHIIdark = ActPAR_photonsm2s * aLHIIdark * FvFm,
         ETRC_WtTau = Sig_m2psii * C_WtTau * ActPAR_photonsm2s,
         ETRqp = Sig_m2psii * qp * ActPAR_photonsm2s,
        ETRqpOxbo = Sig_m2psii * qpOxbo * ActPAR_photonsm2s,
         JVPSII_ETRC_WtTau = ETRC_WtTau * Fomin/Sigmax * ActPAR_photonsm2s,
         JVPSII_ETRqp = ETRqp * Fomin/Sigmax * ActPAR_photonsm2s,
         JVPSII_ETRqpOxbo = ETRqpOxbo * Fomin/Sigmax * ActPAR_photonsm2s
        )

       
 head(SolFitsTrim2)
```

```{r prelimplots2}

SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = ETRqpOxbo, colour = MeasureO2_uM)) +
  geom_line(aes(x = ActPARCorr, y = ETRqpOxbo, colour = MeasureO2_uM)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
  theme_bw()


SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ETRqp, y = ETRqpOxbo, colour = MeasureO2_uM)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(ratio = 1) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 


SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = C_WtTau, y = qpOxbo, colour =  MeasureO2_uM)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(xlim = c(0,1), ylim = c(0,1), ratio = 1) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 



SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x =  JVPSII_aLHIIminmax, y = JVPSII_ETRqpOxbo, colour = MeasureO2_uM)) +
  #scale_colour_manual(values = Colours_nm) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #coord_fixed(ratio = 1) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 


```
Merge SolFitsTrim with MetaData & Turner Chl Data 
# Merge OLISSpectra with MetaData and ChlData
```{r SolFitsTrim with MetaData and ChlData}

SolFitsMeta <- SolFitsTrim2 %>%
  left_join(., MetaData, join_by(CultureID == ID)) |>
   mutate(O2_uM = case_when(O2 == 0 ~ 2,
                           O2 == 1 ~ 25,
                           O2 == 21 ~ 250)) |>
  select(-c("Description", "Motivation", "doi", "Par_ueAdjusted", "DateOfAdjustment", "ElaspedHoursAtAdjustment", "...44", "...45")) 

    
SolFitsMeta <- SolFitsMeta |>
  left_join(ChlData, join_by(CultureID == CultureID))
        
SolFitsMeta |>
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = FvFm)) +
  facet_grid(cols = vars(Strain), rows = vars(Par_ue, O2_uM)) +
  theme_bw()            

```


```{r save SolFitsTrim data}
saveRDS(SolFitsMeta, file.path(DataOut, paste(Project, Run, "SolFitsMeta.Rds", sep = "_"), fsep = .Platform$file.sep))
```


