---
title: "SolisenseImport"
author:
- Maximilian Berthold
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE   
csl: plos-one.csl
---


test 

This .Rmd imports and tidys fit data from the Solisense kinetic fluorometer software.
It does not perform the underlying fits of the induction/relaxation profiles from FRRf protocols.

# Done
Corrected values for Excitation; this 'happens' during the re-fit if the proper calibration file settings are chosen
  Refit needs to be done separately for data from Cuvette & Data from water jacket; TC/no TC will need to be segregated somehow.
  
Corrected values for ActPAR for cuvette (no TC) and for jacket (TC)
  Recalibration for ActPAR to ActPARCorr done post-hoc herein

Add more ETR estimators  
  
# Set Chunk Options


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Set Project Variables
```{r set project variables}
Project <- "FluorO2"
DataOut <- file.path("..", "ImportData", "FRRf")
CalibData <- file.path("..", "CalibrationData")

Run <- "MiSaProchloro"

DataIn <- file.path("..", "RawData", "MiSa", "Solisense", fsep = .Platform$file.sep)

FileID <- "fit"

FileEncode <- "UTF-8" 
Delimiter <- ","

HeaderRows <- 0

```

```{r conversions}
us_s <- 1000000
photons_umol <- 6.022E17
A2_m2 <- 1E20
```


```{r load libraries}
library(tidyverse)
library(lubridate)
library(photobiologyWavebands) #R colours from nm values
library(broom) #formatting model outputs

#https://googlesheets4.tidyverse.org/
# library(googledrive)
# library(googlesheets4)

```

```{r read ActPAR calibration files}
#ActPARCal <- readRDS("~/Dropbox/CampbellLabProtocols/ChlorophyllFluorescence/SolisenseInformation/SolisenseInformation_DCCalibParam.Rds")

ActPARCrossCal <- list.files(path = CalibData, full.names = TRUE)  %>%
       map_df(~readRDS(file  = .))

#intercept set to 0 in lm in SolisenseInformation.Rproj/SolisenseCalibCompare.Rmd
ActPARCrossCal <- ActPARCrossCal |>
  rename(#Intercept = `estimate_(Intercept)`,
         Slope = `estimate_LIFT_Gen_Developer.cal`,
         #Intercept_SE = `std.error_(Intercept)`,
         Slope_SE = `std.error_LIFT_Gen_Developer.cal`)
```

```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c(w_length2rgb(445), w_length2rgb(470), w_length2rgb(505),  w_length2rgb(535), w_length2rgb(590))
names(Colours_nm) <-  Wavelengths_nm

```

```{r list PSI files for file import}
SolisenseFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE, recursive = FALSE)

SolisenseFiles

#test for duplicate file names
unique(duplicated(SolisenseFiles))
```


```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
#design choice 2 file reading functions or add a filetype variable to a single function
#stringsAsFactors =FALSE somewhere? 
# 
# read.delim_plus <- function(flnm, file_encode, delimiter, header_rows){read.delim(flnm, fileEncoding = file_encode, sep = delimiter,  skip = header_rows, row.names = NULL) %>% mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))
# }

#a read function using tidyverse::read_delim that skips a fixed number of header rows, and adds columns to the dataframe containing the filename and the file creation date time.
read_delim_plus <- function(flnm, delimiter, headerrows, fileencode){read_delim(flnm, delim = delimiter,  col_names = TRUE,  skip = headerrows, escape_double = FALSE,  locale = locale(encoding = fileencode), trim_ws = TRUE) %>%
    mutate(Filename = flnm)
  }


```

Read Test File
```{r read example Solisense file}
#issue with rows with --------;  easy to filter though
# TestFile <- read.delim_plus(flnm = "../RawData/Solisense/MURIS_202105121400_MaBe3414_445_caloxy_fit.csv", file_encode = FileEncode, delimiter = Delimiter, header_rows = HeaderRows)

```

purrr::map to read all files
```{r read Solisense files}
SolFits <- SolisenseFiles %>%
  map_df(~read_delim_plus(flnm =., delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode))

head(SolFits)
colnames(SolFits)

```


```{r tidy SolFitsTrim}
#Think of better ways to do this

SolFitsTrim <- SolFits %>% 
  filter(!grepl("----", DATE)) %>% # remove rows with "----" in DATE
  select(-c("RFID_User_Data", "Barcode_Data", "PIF",  "Lon", "Lat", "GPS_stat", "Dur-Wat", "PQP_Size", `...39`, "Alpha", "Ek", "Pmax" )) %>% # remove superfluous columns
  mutate(Filename = str_remove(string = Filename, pattern = "../RawData/MiSa/Solisense/"),
         Filename = str_remove(string = Filename, pattern = "_caloxy"),
         Filename = str_remove(string = Filename, pattern = "_refit.csv")
         ) %>%
  separate(Filename, into = c("Project", "RunDateTime", "CultureID", "Ex_WL"), sep = "([\\/\\_])", remove = FALSE) %>%
  mutate(RunDateTime = ymd_hm(RunDateTime), 
         TIME = as.character(TIME)) %>%  #time-column may be read in as factor, and as.character changes it to numeric; using lubdridate::hms would only change the format to 13H 4M 2S but does not work later to merge into one DateTime-column
  rename(SourceDataFile = `Source DataFile`,
         ObsDate = DATE,
         ObsTime = TIME,
         FvFm = "Fv/Fm") %>%
  mutate(Ex_WL = as.factor(as.numeric(Ex_WL))) %>%
  mutate(FvFm = as.numeric(as.character(FvFm)),
         nm445 = as.numeric(as.character(Light_1)),
         nm470 = as.numeric(as.character(Light_2)),
         nm505 = as.numeric(as.character(Light_3)),
         nm535 = as.numeric(as.character(Light_4)),
         nm590 = as.numeric(as.character(Light_5)),
         IR = as.numeric(as.character(Light_6))
         ) %>%
  rename(StartDateTimeSol = RunDateTime) %>%
  drop_na(StartDateTimeSol) %>%
  mutate(ObsTime = hms(ObsTime),
         ObsDate = ymd(ObsDate)) %>%
  mutate(ObsDateTime = ymd_hms(paste(ObsDate, ObsTime))) %>%
  relocate(ObsDateTime, .after = ObsTime) %>%
  relocate(CultureID, .before = ObsDate) 

#for consistency add TempCont column
SolFitsTrim <- SolFitsTrim %>%
  mutate(TempCont = "TC")

head(SolFitsTrim)
```


```{r actparcorr}
#Add ActPARcorr with proper correction factors for TC and no TC
#Intercepts for cross conversions set to 0.

#Some smarter way to do this with map etc....
SolFitsTrim <- SolFitsTrim |> 
  mutate(nm445Corr = case_when(TempCont == "TC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm445 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr1_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
         nm470Corr = case_when(TempCont == "TC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm470 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr2_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
         nm505Corr = case_when(TempCont == "TC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm505 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr3_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
           nm535Corr = case_when(TempCont == "TC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm535 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr4_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
          nm590Corr = case_when(TempCont == "TC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ nm590 * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "Pwr5_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]),
          IRCorr = case_when(TempCont == "TC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCWaterJacketlm_tidy"],
                                 TempCont == "noTC" ~ IR * ActPARCrossCal$Slope[ActPARCrossCal$DCLamp == "PwrIR_uE" & ActPARCrossCal$Models == "DCCuvettelm_tidy"]))

head(SolFitsTrim)


SolFitsTrim <- SolFitsTrim %>%
  mutate(across(.cols = c(Light_1:CarQ), .fns = as.numeric)) %>%
  mutate(ActPAR = nm445 + nm470 + nm505 + nm535 + nm590 + IR) |>
  mutate(ActPARCorr = nm445Corr + nm470Corr + nm505Corr + nm535Corr + nm590Corr + IRCorr)#better ways to do this?

```

```{r durations}
#generate column with duration of light step in s
#add a column adding Dark1s based upon any step < 5 s
#replace NA for first dark with nominal 181;  issue will be changing durations of light steps across each run
SolFitsTrim <- SolFitsTrim %>%
  group_by(SourceDataFile, Filename, Project, CultureID, ObsDate, Ex_WL, TempCont) %>%
  #mutate(Step_s = as.numeric(ObsDateTime - lag(ObsDateTime)), .after = ObsDateTime) %>%
  mutate(Step_s = replace_na(as.numeric(ObsDateTime - lag(ObsDateTime)), 181), .after = ObsDateTime) %>% 
  mutate(LR_s = as.numeric(ObsDateTime - ObsDateTime[1]), .after = Step_s) %>%
  mutate(Dark1s = if_else(Step_s > 5, 0, 1), .after = Step_s) %>%
  relocate(Ex_WL, .after = Dark1s) %>%
  relocate(ActPAR, .after = Ex_WL) %>%
  ungroup()
#Figure out how to cope with final step at 0 PAR, not followed by Dark1s step
#separate Dark1s rows
#Figure out how to re-match Dark1s to appropriate light steps

```

```{r}
# test <- SolFitsTrim %>%
#   filter(Ex_WL == "505" & CultureID == "SySl1191")
```


```{r prelimplots}
SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  filter(Tau2QA < 20000) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = FvFm, colour = as.factor(TempCont))) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  filter(Dark1s == 0) %>%
  filter(Tau2QA < 20000) %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = Tau2QA, colour = as.factor(TempCont), size = LR_s)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw()

SolFitsTrim %>%
  #filter(Dark1s != 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = Alp2QA, colour = as.factor(TempCont), size = LR_s)) +
  #scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme_bw() 

```

Oxborough & Baker 1997 for Fo'
```{r estimate parameters}
#think about nest_by and map?
SolFitsTrim2 <- SolFitsTrim %>%
  mutate(WtTau = ((Alp1QA * Tau1QA) + (Alp2QA * Tau2QA) + (Alp3QA * Tau3QA)),
         InvWtTau = 1/WtTau,
         Sig_m2psii = Sig/1E20,
         ActPAR_photonsm2s = ActPAR *  6.022e17,
         C_WtTau = 1/(1 + (Sig_m2psii * ActPAR_photonsm2s * (WtTau /1000000)))
         ) %>%
  nest(.by = c(CultureID, Ex_WL, SourceDataFile, Filename, ObsDate )) %>%
   mutate(Fodark = map(data, ~.$Fo[1]),
          Fmdark = map(data, ~.$Fm[1]),
          Fomin = map(data, ~min(.$Fo, na.rm = TRUE)), 
          Fmmax = map(data, ~max(.$Fm, na.rm = TRUE)),
          Sigdark = map(data, ~.$Sig[1]),
          Sigmax = map(data, ~max(.$Sig, na.rm = TRUE)),
          qp = map(data, ~(.$Fm - .$Fo)/(.$Fm - lead(.$Fo)))
          ) %>%
  unnest(cols = c(data, Fodark,Fmdark,Fomin, Fmmax,Sigdark,Sigmax, qp)) %>%
  mutate(aLHIIdark = (Fmdark * Fodark)/(Fmdark - Fodark),
         aLHIIminmax = (Fmmax * Fomin)/(Fmmax - Fomin),
         FoOxbo = Fomin/(((Fmmax - Fomin)/Fmmax) + (Fomin/Fm)),
         qpOxbo = (Fm - Fo)/(Fm - FoOxbo),
         JVPSII_aLHIIminmax = ActPAR_photonsm2s * aLHIIminmax * FvFm,
         JVPSII_aLHIIdark = ActPAR_photonsm2s * aLHIIdark * FvFm,
         ETRC_WtTau = Sig_m2psii * C_WtTau * ActPAR_photonsm2s,
         ETRqp = Sig_m2psii * qp * ActPAR_photonsm2s,
        ETRqpOxbo = Sig_m2psii * qpOxbo * ActPAR_photonsm2s,
         JVPSII_ETRC_WtTau = ETRC_WtTau * Fomin/Sigmax * ActPAR_photonsm2s,
         JVPSII_ETRqp = ETRqp * Fomin/Sigmax * ActPAR_photonsm2s,
         JVPSII_ETRqpOxbo = ETRqpOxbo * Fomin/Sigmax * ActPAR_photonsm2s
        )

       
 head(SolFitsTrim2)
```

```{r prelimplots2}

SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = ETRqpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 


SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = ETRqp, y = ETRqpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(ratio = 1) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 


SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x = C_WtTau, y = qpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  coord_fixed(xlim = c(0,1), ylim = c(0,1), ratio = 1) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 



SolFitsTrim2 %>%
  filter(Dark1s == 0) %>%
  ggplot() +
  geom_point(aes(x =  JVPSII_aLHIIminmax, y = JVPSII_ETRqpOxbo, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") + 
  #coord_fixed(ratio = 1) +
  facet_grid(cols = vars(Ex_WL), rows = vars(CultureID)) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) 


```


```{r save SolFitsTrim data}
saveRDS(SolFitsTrim2, file.path(DataOut, paste(Project, Run, "SolFitsTrim.Rds", sep = "_"), fsep = .Platform$file.sep))
```


